---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# odyssey

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Access data and download documents from the [Open Archive HAL](https://hal.archives-ouvertes.fr/). This package provides a programmatic access to the [HAL API](https://api.archives-ouvertes.fr/docs).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("nfrerebeau/odyssey")
```

## Usage

```{r package}
library(odyssey)
library(magrittr)
```

The use of **odyssey** involves three steps. First, a standard query is created using `hal_api()`. Then, a set of functions allows to customize this query (see below). Finally, `hal_search()` and `hal_download()` allow to collect data and to download documents.

The following functions allow you to customize a query. They must be applied to the object returned by `hal_api()` and can be called in any order. `hal_filter` can be used several times to add multiple search filters. See the HAL search API documentation for a [list of available fields](https://api.archives-ouvertes.fr/docs/search/?schema=fields#fields).

* `hal_query()` allows to choose the fields to query and to define the query terms using boolean logic (`q` parameter). For a simple search, grouping terms in a list allows to combine them with AND, while grouping terms in a vector allows to combine all the terms with OR. If needed, the infix functions `%AND%`, `%OR%`, `%NOT%`, `%IN%`, `%TO%` allow to build more complex queries (remember that infix operators are composed left to right).
* `hal_select()` is used to select the fields to be returned in the results (`fl` parameter).
* `hal_filter()` is used to [retain all results that satisfy a conditions](https://api.archives-ouvertes.fr/docs/search/?#fq) (`fq` parameter).
* `hal_sort()` [orders the results](https://api.archives-ouvertes.fr/docs/search/?#sort) by the value of the select field (`sort` parameter). According to the HAL API documentation, you should avoid text fields and multi-valued fields which will produce unpredictable results.
* `hal_group()` is used to [group results](https://api.archives-ouvertes.fr/docs/search/?#group) (`group.*` parameters).
* `hal_facet()` ...forthcoming.

Get the 10 most recent documents about archaeology of Celts in France:

```{r search}
## Topic selection
## Will be combined with AND
topic <- list("archéologie", "Celtes", "France")

## Search publications
hal_api() %>%
  hal_query(topic) %>%
  hal_select("title_s", "producedDate_tdate") %>%
  hal_filter("notice" %IN% "submitType_s") %>% 
  hal_sort("producedDate_tdate", decreasing = TRUE) %>%
  hal_search(limit = 10)
```

Get the most recent archaeological publication (in French) by journal:

```{r group}
hal_api() %>%
  hal_query("archéologie") %>%
  hal_select("producedDate_tdate") %>%
  hal_filter("ART" %IN% "docType_s") %>%
  hal_sort("producedDate_tdate", decreasing = TRUE) %>%
  hal_group(
    field = "journalTitle_s",
    sort = "producedDate_tdate", 
    decreasing = TRUE
  ) %>%
  hal_search(limit = 10)
```

## Contributing
Please note that the **odyssey** project is released with a [Contributor Code of Conduct](https://github.com/nfrerebeau/odyssey/blob/master/.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.
